---
title: "Individual1"
author: "Matthew"
date: "9/19/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


  
  ## Background
  
  Brady Brelinski, Founding Member of the Manhattan Chocolate Society, obviously likes chocolate. He has assembled a database of ratings for plain dark chocolate bars: [Flavors of chocolate](http://flavorsofcacao.com/chocolate_database.html)

By now, over 1900 different chocolate bars have been rated. 

## Meaning of ratings

Flavors of Cacao Rating System:
  
- 5= Elite (Transcending beyond the ordinary limits)
- 4= Premium (Superior flavor development, character and style)
- 3= Satisfactory (3.0) to praiseworthy (3.75) (well made with special qualities)
- 2= Disappointing (Passable but contains at least one significant flaw)
- 1= Unpleasant (mostly unpalatable)


## Question set (individual)

Coordinate with your teammate and decide among you who is Individual 1 and Individual 2, respectively. Each of you should create an RMarkdown file either named `individual1.Rmd` or `individual2.Rmd` to include the answers.

**For each of the questions below provide at least one graphic as a basis for your answer.**
  
  1. How are ratings distributed? Dont forget to mention outliers, if there are any.
    ```{r,eval=TRUE}
plot(choco$Rating,choco$Cocoa.Pct, xlab = "Ratings", ylab = "Cocoa Percentage", pch = 2, cex=2) # creates a plot with Ratings on x-axis and Cocoa Percentage of y-axis. The symbol of points is set to be a triangle (pch=2) and the size of the points is adjusted to be larger (cex=2). 
```
  - the rating are distributed heavaly in the center between 2 and 4 with and looks to be -right scude 
  -  there looks like there could be one outlire at 5  
  
  2. Do ratings depend on the cacao percentage of a chocolate bar? 
    ```{r,eval=TRUE}
plot(choco$Rating,choco$Cocoa.Pct, xlab = "Ratings", ylab = "Cocoa Percentage", pch = 2, cex=2) # creates a plot with Ratings on x-axis and Cocoa Percentage of y-axis. The symbol of points is set to be a triangle (pch=2) and the size of the points is adjusted to be larger (cex=2). 
```
  -  yes there is vary little rating with 50% coco and while most of the rating have around -70% coc those that have 100% have alower than avrage rating compared to the whole group
  
  3. What class is the variable representing company locations? How is this different from a -'character' variable? (You do not need to produce a graphic for this question.)
  - its class is factor
s