---
title: "submit to canvis"
author: "Matthew"
date: "9/19/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## the names of the team members that worked on the document.
Matthew Peterson (matthewp)

## git hub info

a link to the github repo you were working in, https://github.com/MDLeader53/lab2.git
the owner’s Github repo name, Matthew (individual1)
and his/her username. MDLeader53

##team answers for questions 1

```{r, eval=TRUE}
recent_rating = choco[choco$Review.Date>2011,]
# creates recent_rating varable that contains choco review data for all years greater than 2011
unique(recent_rating$Company.Location) # NOTICE: how many countries are listed but how many levels are there? 
# find all the uniqe country locations in recent rating data set- removed any lines of data that had duplate contries 
recent_rating$Company.Location = droplevels(recent_rating$Company.Location)
# removes the empty levels created by the unique methiod call
head(recent_rating)
#shows all of the colunm headers as well as the first 6 rows of data 
cross_table = table(recent_rating$Review.Date,recent_rating$Company.Location)
#creats a table showing all the yearrs there was a rating and the country that the company that was rated was from
cross_table
# desplays the tables
which(cross_table[1,]!=0 & cross_table[2,]!=0 & cross_table[3,]!=0 & cross_table[4,]!=0 & cross_table[5,]!=0)

france_recent = subset(recent_rating,Company.Location =='France')
#creates a varable france_recent that shows the total number of ratings in france 
uk_recent = subset(recent_rating,Company.Location =='U.K.')
#creates a varable france_recent that shows the total number of ratings in UK 
germany_recent = subset(recent_rating,Company.Location=='Germany')
#creates a varable france_recent that shows the total number of ratings in Germany 
par(mfrow=c(2,2))
#definds an empty plot
color1 = ifelse(france_recent$Rating >median(france_recent$Rating), 'blue', 'green')
#sets the colors for the points in the plot
plot(france_recent$Cocoa.Pct ~ france_recent$Review.Date,ylim=c(50,90),col=color1,pch=18,cex=1.5,xlab="Review Date", ylab= "Cocoa Percentage", main= "France") 
# creats a plot of percentage off coco in a cany and the review date for the country France
legend('bottomright',legend=c('High Rating', 'Low Rating'),col=c('blue','green'),pch=18)
#defines the plot legend
color2 = ifelse(uk_recent$Rating >median(uk_recent$Rating), 'purple', 'red')
#sets the colors for the points in the plot
plot(uk_recent$Cocoa.Pct ~ uk_recent$Review.Date,ylim=c(50,90),col=color2,pch=18,cex=1.5, xlab="Review Date", ylab= "Cocoa Percentage", main= "UK")
# creats a plot of percentage off coco in a cany and the review date for the united kingdon of UK
legend('bottomright',legend=c('High Rating', 'Low Rating'),col=c('purple','red'),pch=18)
#defines the plot legend
color3 = ifelse(germany_recent$Rating > median(germany_recent$Rating), 'orange', 'yellow')
#sets the colors for the points in the plot
plot(germany_recent$Cocoa.Pct ~germany_recent$Review.Date,ylim=c(50,90),col=color3,pch=18,cex=1.5,xlab="Review Date", ylab= "Cocoa Percentage", main= "Germany") 
# creats a plot of percentage off coco in a cany and the review date for the German empire
legend('bottomright',legend=c('High Rating', 'Low Rating'),col=c('orange','yellow'),pch=18)
#defines the plot legend
```

##team answers for questions 2
2 \. Click Zoom on the Rstudio window (under Plots) to see the plot more clearly. How do you think the plot produced from the code above can be improved? Recommend at least one possible improvement. 
instead of having the review be eather high or low use a gradeant color scale to show there values or use a 3rd color thats  an ok review. or use  a histagram with the years on the x axes the coco on y-axes and each bucket is a review for that year (grouped by years) and above each bar is the rating 


##team answers for questions 3
-to do by partner (indevidual2)
##team answers for questions 4
-to do by partner (indevidual2)
##team answers for questions 5
-to do by partner (indevidual2)

## Question set (individual1)

Coordinate with your teammate and decide among you who is Individual 1 and Individual 2, respectively. Each of you should create an RMarkdown file either named `individual1.Rmd` or `individual2.Rmd` to include the answers.

**For each of the questions below provide at least one graphic as a basis for your answer.**
  
  1. How are ratings distributed? Dont forget to mention outliers, if there are any.
    ```{r,eval=TRUE}
plot(choco$Rating,choco$Cocoa.Pct, xlab = "Ratings", ylab = "Cocoa Percentage", pch = 2, cex=2) # creates a plot with Ratings on x-axis and Cocoa Percentage of y-axis. The symbol of points is set to be a triangle (pch=2) and the size of the points is adjusted to be larger (cex=2). 
```
  - the rating are distributed heavaly in the center between 2 and 4 with and looks to be -right scude 
  -  there looks like there could be one outlire at 5  
  
  2. Do ratings depend on the cacao percentage of a chocolate bar? 
    ```{r,eval=TRUE}
plot(choco$Rating,choco$Cocoa.Pct, xlab = "Ratings", ylab = "Cocoa Percentage", pch = 2, cex=2) # creates a plot with Ratings on x-axis and Cocoa Percentage of y-axis. The symbol of points is set to be a triangle (pch=2) and the size of the points is adjusted to be larger (cex=2). 
```
  -  yes there is vary little rating with 50% coco and while most of the rating have around -70% coc those that have 100% have alower than avrage rating compared to the whole group
  
  3. What class is the variable representing company locations? How is this different from a -'character' variable? (You do not need to produce a graphic for this question.)
  - its class is factor